\thesistitle

### 2019-06-13 sections/research.tex
Explaining detecting clones

\subsubsection{Detecting Clones}
After building the clone grid, we use it to detect clones. We decided to focus on the detection of clone classes rather than clone pairs because clone pairs do not provide a general overview of all entities containing the clones, with all their related issues and characteristics \cite{fontana2012duplicated}. Although clone classes are harder to manage, they provide all information needed to plan a suitable refactoring strategy, since this way all instances of a clone are considered. Another issue that results from grouping clones by pairs: clone reference amount increases according to the binomial coefficient formula (two clones form a pair, three clones form three pairs, four clones form six pairs, and so on), which causes a heavy information redundancy \cite{fontana2012duplicated}.

@@

Using the example shown in figure \ref{fig:clonegrid} we can explain how we detect clones. Suppose we are currently finding clones at the purple marked box. We then follow all ``duplicate'' relations until we have found all clones (the boxes marked in green). We now have a single statement clone class. Next, we move to the previous line. Here again, we collect all duplicates of this node. For each of these duplicates, we check whether the node following it is already in the clone class we collected in the previous iteration. In this case, only two of the

>>>>

We generally call the declarations and statements represented in this grid \textit{nodes}. The relations \textit{next} and \textit{previous} in this grid are represented as an undirected relation. The relations representing duplicated are directed. This is a restriction we've chosen as it creates an important constraint for the clone detection process. This process is explained in section \ref{sec:detectingclones}.

\subsubsection{Comparing Statements/Declarations}
In the previous section we described ...

\subsubsection{Detecting Clones} \label{sec:detectingclones}
After building the clone grid, we use it to detect clones. We decided to focus on the detection of clone classes rather than clone pairs because clone pairs do not provide a general overview of all entities containing the clones, with all their related issues and characteristics \cite{fontana2012duplicated}. Although clone classes are harder to manage, they provide all information needed to plan a suitable refactoring strategy, since this way all instances of a clone are considered. Another issue that results from grouping clones by pairs: clone reference amount increases according to the binomial coefficient formula (two clones form a pair, three clones form three pairs, four clones form six pairs, and so on), which causes a heavy information redundancy \cite{fontana2012duplicated}.

@@

Using the example shown in figure \ref{fig:clonegrid} we can explain how we detect clones. Suppose we are finding clones for two files and the final node of the second file is a variable declarator. This final node is represented in the example figure by the purple box (1). We then follow all ``duplicate'' relations until we have found all clones (2 and 3). We now have a single statement clone class of three clone instances (1, 2 and 3). Next, we move to the previous line (4). Here again, we collect all duplicates of this node (4 and 5). For each of these duplicates, we check whether the node following it is already in the clone class we collected in the previous iteration. In this case, (2) follows (5) and (1) follows (4). This means that node (3) does not form a 'chain' with other cloned statements. Because of this, the clone class of (1, 2 and 3) comes to an end. It will be checked against the thresholds, and if adhering to the threshold, considered a clone. We then go further to yet the previous node (6). In this case, this node does not have any clones. This means we check the (2 and 5, 1 and 4) clone class against the thresholds, and if it adheres, consider it a clone. Dependent on the thresholds, we'd now have found two clone classes.

The grid representation shown in figure \ref{fig:clonegrid} is only shown as a grid for ease of comprehension. In fact, it is not a grid, but a graph. Eventually, following only the ``previous node'' relations, we can get from (6) to (2). When we are at that point, we will find only one cloned node for (2), namely (3). However, after we check this clone against the thresholds, we check whether it is a subset of any exisiting clone. If this is the case, we discard the clone.
